---
output:
  html_document
params:
  epoch: "enrol"
  map_id: "001"
---

<style type="text/css">
  body{
    font-size:  9pt;
  }
  h1{
    font-size: 18pt;
  }
  h2{
    font-size: 14pt;
  }
  h3,h4,h5,h6{
    font-size: 12pt;
  }
</style>

# Vanderbilt Memory & Aging Project: Neuropsychological Data Summary Sheet

```{r setup, include = FALSE}
library(kableExtra)

data.df <- complete_enrollment_data.df[complete_enrollment_data.df$map_id == params$map_id, ]
data.df <- map_df(1:nrow(data.df), ~compute_scores(data.df[., ]))

np.df <- data.df[data.df$epoch == params$epoch, ]

tables.list <- generate_tables(np.df)

knitr::opts_chunk$set(echo = FALSE)
options(knitr.kable.NA = "--")
```

```{r}
tables.list[["metadata_wide.df"]] %>%
  knitr::kable(., align = 'ccccc', col.names = NULL, table.attr = "style='width:90%;'") %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  row_spec(c(1, 3), bold = T)
```

:::: {style="display: flex; justify-content: space-evenly;"}

::: {style="padding: 1pt;"}

## Global Cognition: MOCA

```{r}
knitr::kable(tables.list[["moca.df"]], digits = 1, align = 'lrr') %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(
    1:3, 
    color = replace_na(ifelse(tables.list[["moca.df"]]$interpretation == "Impaired", "red", "black"), "black"),
    italic = replace_na(ifelse(tables.list[["moca.df"]]$interpretation == "Impaired", TRUE, FALSE), FALSE)
  )
```

## Learning & Memory

### CVLT-II

```{r}
knitr::kable(tables.list[["cvlt.df"]], digits = 1, align = 'lrr') %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(
    1:3, 
    color = replace_na(ifelse(tables.list[["cvlt.df"]]$scaled_score <= -1.5, "red", "black"), "black"),
    italic = replace_na(ifelse(tables.list[["cvlt.df"]]$scaled_score <= -1.5, TRUE, FALSE), FALSE)
  )
```

### Biber

```{r}
knitr::kable(tables.list[["biber.df"]], digits = 1, align = 'lrr') %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(
    1:3, 
    color = replace_na(ifelse(c(tables.list[["biber.df"]]$scaled_score[1:9] <= -1.5, rep(FALSE, 4)), "red", "black"), "black"),
    italic = replace_na(ifelse(c(tables.list[["biber.df"]]$scaled_score[1:9] <= -1.5, rep(FALSE, 4)), TRUE, FALSE), FALSE)
  )
```

## Language

### BNT-30 item (even)

```{r}
knitr::kable(tables.list[["bnt.df"]], digits = 1, align = 'lrr') %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(
    1:3, 
    color = replace_na(ifelse(tables.list[["bnt.df"]]$scaled_score <= -1.5, "red", "black"), "black"),
    italic = replace_na(ifelse(tables.list[["bnt.df"]]$scaled_score <= -1.5, TRUE, FALSE), FALSE)
  )
```

### Animals

```{r}
knitr::kable(tables.list[["animals.df"]], digits = 1, align = 'lrr') %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(
    1:3, 
    color = replace_na(ifelse(tables.list[["animals.df"]]$scaled_score <= 35, "red", "black"), "black"),
    italic = replace_na(ifelse(tables.list[["animals.df"]]$scaled_score <= 35, TRUE, FALSE), FALSE)
  )
```

## Mood: GDS

```{r}
knitr::kable(tables.list[["gds.df"]], digits = 1, align = 'lrr') %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(
    1:3, 
    color = replace_na(ifelse(tables.list[["gds.df"]]$score >= 10, "red", "black"), "black"),
    italic = replace_na(ifelse(tables.list[["gds.df"]]$score >= 10, TRUE, FALSE), FALSE)
  )
```

## Visuospatial Skills: HVOT

```{r}
knitr::kable(tables.list[["hvot.df"]], digits = 1, align = 'lrr') %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(
    1:3, 
    color = replace_na(ifelse(tables.list[["hvot.df"]]$scaled_score >= 65, "red", "black"), "black"),
    italic = replace_na(ifelse(tables.list[["hvot.df"]]$scaled_score >= 65, TRUE, FALSE), FALSE)
  )
```

:::

::: {style="padding: 1pt;"}

## Attention/Executive Functioning/Information Processing

### DKEFS: Trail Making Test

```{r}
knitr::kable(tables.list[["dkefs_trail.df"]], digits = 1, align = 'lrr') %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) 
  # column_spec(
  #   1:3, 
  #   color = ifelse(tables.list[["dkefs_trail.df"]]$scaled_score <= 5, "red", "black"),
  #   italic = ifelse(tables.list[["dkefs_trail.df"]]$scaled_score <= 5, TRUE, FALSE)
  # )
```

### DKEFS: Color-Word

```{r}
knitr::kable(tables.list[["dkefs_color.df"]], digits = 1, align = 'lrr') %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

### COWA

```{r}
knitr::kable(tables.list[["cowa.df"]], digits = 1, align = 'lrr') %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

### Tower Test

```{r}
knitr::kable(tables.list[["tower.df"]], digits = 1, align = 'lrr') %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

### Digit Symbol Coding

```{r}
knitr::kable(tables.list[["digit_symbol.df"]], digits = 1, align = 'lrr') %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

### Mental Control

```{r}
knitr::kable(tables.list[["mc1.df"]], digits = 2, align = 'lrrrr') %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

```{r}
knitr::kable(tables.list[["mc2.df"]], digits = 2, align = 'lrr') %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

### WMS-IV Symbol Span

```{r}
knitr::kable(tables.list[["symbol_span.df"]], digits = 1, align = 'lrr') %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

:::

::::

## Notes

```{r, results = 'asis'}
cat(np.df$np_notes)
```
