---
output:
  html_document
params:
  vmac_id: "001"
---

<style type="text/css">
  body{
    font-size:  9pt;
  }
  h1{
    font-size: 18pt;
  }
  h2{
    font-size: 14pt;
  }
  h3,h4,h5,h6{
    font-size: 12pt;
  }
</style>

# Vanderbilt Memory & Aging Project: Neuropsychological Data Summary Sheet - Eligibility

```{r setup, include = FALSE}
library(kableExtra)
source("~/dev/lureka/eligibility/R/compute_scores.R")

data.df <- complete_eligibility_data.df[complete_eligibility_data.df$vmac_id == params$vmac_id, ]

tables.list <- generate_tables(data.df)

knitr::opts_chunk$set(echo = FALSE)
options(knitr.kable.NA = "--")
```

```{r}
tables.list[["metadata_wide.df"]] %>%
  knitr::kable(., align = 'ccccc', col.names = NULL, table.attr = "style='width:90%;'") %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  row_spec(c(1, 3), bold = T)
```

:::: {style="display: flex; justify-content: space-evenly;"}

::: {style="padding: 1pt;"}

## Global Cognition

### MOCA

```{r}
knitr::kable(tables.list[["moca.df"]], digits = 1, align = 'lrr') %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(
    1:3, 
    color = replace_na(ifelse(tables.list[["moca.df"]]$interpretation == "Impaired", "red", "black"), "black"),
    italic = replace_na(ifelse(tables.list[["moca.df"]]$interpretation == "Impaired", TRUE, FALSE), FALSE)
  )
```

### CDR

```{r}
knitr::kable(tables.list[["cdr.df"]], digits = 1, align = 'lrr') %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

## Learning & Memory

### SRT

```{r}
knitr::kable(tables.list[["srt.df"]], digits = 1, align = 'lrr') %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(
    1:3, 
    color = replace_na(ifelse(abs(tables.list[["srt.df"]]$scaled_score) >= 1.5, "red", "black"), "black"),
    italic = replace_na(ifelse(abs(tables.list[["srt.df"]]$scaled_score) >= 1.5, TRUE, FALSE), FALSE)
  )
```

### BVRT

```{r}
knitr::kable(tables.list[["bvrt.df"]], digits = 1, align = 'lrr') %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(
    1:3, 
    color = replace_na(ifelse(abs(tables.list[["bvrt.df"]]$scaled_score) >= 1.5, "red", "black"), "black"),
    italic = replace_na(ifelse(abs(tables.list[["bvrt.df"]]$scaled_score) >= 1.5, TRUE, FALSE), FALSE)
  )
```

## Attention: WAIS-III Digit Span

```{r}
digit_span_output.df <- knitr::kable(tables.list[["digit_span.df"]], digits = 1, align = 'lrr') %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(
    1:3, 
    color = replace_na(ifelse(tables.list[["digit_span.df"]]$scaled_score <= -1.5, "red", "black"), "black"),
    italic = replace_na(ifelse(tables.list[["digit_span.df"]]$scaled_score <= -1.5, TRUE, FALSE), FALSE)
  )

if (pull(tables.list[["digit_span.df"]][3, 3]) < 6) {
  digit_span_output.df %>%
    row_spec(
      3,
      color = "red",
      italic = TRUE
    )
} else {
  digit_span_output.df
}
```

## Effort: Rey 15 Item Test

```{r}
knitr::kable(tables.list[["rey15.df"]], digits = 1, align = 'lrr') %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

:::

::: {style="padding: 1pt;"}

## Estimated Pre-Morbid Intelligence: WRAT-3 Reading

```{r}
knitr::kable(tables.list[["wrat3_reading.df"]], digits = 1, align = 'lrrr') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(
    1:4, 
    color = replace_na(ifelse(tables.list[["wrat3_reading.df"]]$scaled_score < 78, "red", "black"), "black"),
    italic = replace_na(ifelse(tables.list[["wrat3_reading.df"]]$scaled_score < 78, TRUE, FALSE), FALSE)
  )
```

## Visuospatial Skills: WAIS-IV Block Design

```{r}
knitr::kable(tables.list[["block_design.df"]], digits = 1, align = 'lrr') %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(
    1:3, 
    color = replace_na(ifelse(tables.list[["block_design.df"]]$scaled_score < 6, "red", "black"), "black"),
    italic = replace_na(ifelse(tables.list[["block_design.df"]]$scaled_score < 6, TRUE, FALSE), FALSE)
  )
```

## Language

### BNT-30 Item (Odd)

```{r}
knitr::kable(tables.list[["bnt.df"]], digits = 1, align = 'lrr') %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(
    1:3, 
    color = replace_na(ifelse(abs(tables.list[["bnt.df"]]$scaled_score) >= 1.5, "red", "black"), "black"),
    italic = replace_na(ifelse(abs(tables.list[["bnt.df"]]$scaled_score) >= 1.5, TRUE, FALSE), FALSE)
  )
```

### Vegetables

```{r}
knitr::kable(tables.list[["vegetables.df"]], digits = 1, align = 'lrr') %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(
    1:3, 
    color = replace_na(ifelse(abs(tables.list[["vegetables.df"]]$scaled_score) >= 1.5, "red", "black"), "black"),
    italic = replace_na(ifelse(abs(tables.list[["vegetables.df"]]$scaled_score) >= 1.5, TRUE, FALSE), FALSE)
  )
```

## Executive Functioning/Information Processing

### Trail Making Test

```{r}
knitr::kable(tables.list[["trail.df"]], digits = 1, align = 'lrr') %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(
    1:3, 
    color = replace_na(ifelse(tables.list[["trail.df"]]$scaled_score < 6, "red", "black"), "black"),
    italic = replace_na(ifelse(tables.list[["trail.df"]]$scaled_score < 6, TRUE, FALSE), FALSE)
  )
```

### Stroop

```{r}
knitr::kable(tables.list[["stroop.df"]], digits = 1, align = 'lrr') %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(
    1:3, 
    color = replace_na(ifelse(tables.list[["stroop.df"]]$scaled_score < 6, "red", "black"), "black"),
    italic = replace_na(ifelse(tables.list[["stroop.df"]]$scaled_score < 6, TRUE, FALSE), FALSE)
  )
```

### COWA

```{r}
knitr::kable(tables.list[["cowa.df"]], digits = 1, align = 'lrr') %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(
    1:3, 
    color = replace_na(ifelse(tables.list[["cowa.df"]]$scaled_score < 6, "red", "black"), "black"),
    italic = replace_na(ifelse(tables.list[["cowa.df"]]$scaled_score < 6, TRUE, FALSE), FALSE)
  )
```

<!-- ## Mood: GDS -->

<!-- ```{r} -->
<!-- knitr::kable(tables.list[["gds.df"]], digits = 1, align = 'lrr') %>%  -->
<!--   kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>% -->
<!--   column_spec( -->
<!--     1:3,  -->
<!--     color = replace_na(ifelse(tables.list[["gds.df"]]$score >= 10, "red", "black"), "black"), -->
<!--     italic = replace_na(ifelse(tables.list[["gds.df"]]$score >= 10, TRUE, FALSE), FALSE) -->
<!--   ) -->
<!-- ``` -->

:::

::::

## Notes

```{r, results = 'asis'}
cat(data.df$np_notes)
```
